---
title: "Return_Policy_Effect_BMS"
author: Greg Murray
---


# Policy change impact on bms returns.
#Model 0 OLS; dependent variable=return_amt; key independent variables=post_policy,study_group, #post_policy*studygroup 

### Libraries and Dependencies
```{r}
library(QuantPsyc)
library(effects)
library(MASS)
library(usdm)
library(lmtest)
library(AER)
library(foreign)
library(aod)
library(ggplot2)
library(sandwich)
library(VIF)
library(msm)
```
### Data Initialization
```{r}
setwd('c:/users/greg/r_projects/bus_analytics_project')
bms_returns<-read.csv('bms_return_data3.csv')
summary(bms_returns)
bms_returns$return_amt[is.na(bms_returns$return_amt)]<-0
bms_returns<-na.omit(bms_returns)

colnames(bms_returns)[1]<-"store_number"

BMS_RETURNS_BACKUP<-bms_returns

bms_returns<-BMS_RETURNS_BACKUP
```
### Raw Data Analysis
```{r}
summary(bms_returns)

hist(bms_returns$return_amt)
hist(log(bms_returns$return_amt+1))#
hist(bms_returns$monthly_sales_amt)
hist(log(bms_returns$monthly_sales_amt))#
hist(bms_returns$monthly_sales_cnt) 
hist(log(bms_returns$monthly_sales_cnt))#
hist(bms_returns$store_number_of_skus)
hist(log(bms_returns$store_number_of_skus))#
hist(bms_returns$sa_avg_years_of_exp)
hist(log(bms_returns$sa_avg_years_of_exp))#
hist(bms_returns$avg_length_residence)#
hist(log(bms_returns$avg_length_residence))
hist(bms_returns$cust_gender) 
hist(log(bms_returns$cust_gender))#
hist(bms_returns$homeowner_ratio) 
hist(log(bms_returns$homeowner_ratio+1))#
hist(bms_returns$child_ratio) #
hist(log(bms_returns$child_ratio+1))
```
#### Raw data plots with dependent var
```{r}
sg<-subset(bms_returns, study_group==1)
cg<-subset(bms_returns, study_group==0)
boxplot(bms_returns$return_amt~bms_returns$study_group, xlab="study group") 
```
>##### Returns slightly higher for study group in raw data as expected
```{r}
boxplot(log(sg$return_amt+1)~sg$post_policy,xlab="post_policy (study group)")
```
>##### Returns go down after policy change in the study group (sans regression modelling)
```{r}
boxplot(log(cg$return_amt+1)~cg$post_policy,xlab="post_policy (control group")
```
>##### Returns go down up slightly after policy change in the control group (sans regression modelling)

```{r}
plot(log(bms_returns$monthly_sales_cnt+1), log(bms_returns$return_amt+1))
plot(log(bms_returns$monthly_sales_amt+1), log(bms_returns$return_amt+1))
plot(bms_returns$store_average_price, log(bms_returns$return_amt+1))
plot(bms_returns$store_number_of_skus, log(bms_returns$return_amt+1))
plot(bms_returns$sa_gender, log(bms_returns$return_amt+1))
plot(bms_returns$sa_full_time, log(bms_returns$return_amt+1))
plot(log(bms_returns$sa_avg_years_of_exp), log(bms_returns$return_amt+1))
plot(bms_returns$sa_married, log(bms_returns$return_amt+1))
plot(bms_returns$sa_avg_rate_of_pay, log(bms_returns$return_amt+1))
plot(bms_returns$sa_dependent, log(bms_returns$return_amt+1))
boxplot(log(bms_returns$return_amt+1)~bms_returns$sales_volume_group, xlab="sales volume group")
plot(bms_returns$avg_length_residence, log(bms_returns$return_amt+1))
plot(bms_returns$homeowner_ratio, log(bms_returns$return_amt+1))
plot(bms_returns$child_ratio, log(bms_returns$return_amt+1))
boxplot(log(bms_returns$return_amt+1)~bms_returns$avg_income_code, xlab="avg income code")
boxplot(log(bms_returns$return_amt+1)~bms_returns$avg_age_band, xlab="avg age band")
boxplot(log(bms_returns$return_amt+1)~bms_returns$, xlab="avg income code")
```
#### Stepwise Control Variable Selection
```{r}
OLSModel<-lm(log(return_amt+1)~post_policy+study_group+log(monthly_sales_amt+1)+log(store_average_price+1)+log(store_number_of_skus+1)+sa_gender+sa_full_time+log(sa_avg_years_of_exp+1)+sa_married+sa_avg_rate_of_pay+sa_dependent+avg_income_code+homeowner_ratio+avg_length_residence+child_ratio+avg_age_band+cust_gender+post_policy*study_group, data=bms_returns)

step<-stepAIC(OLSModel, direction="both") #choose vars
step$anova

model_step<-lm(log(return_amt+1)~post_policy+study_group+log(monthly_sales_amt+1)+store_average_price+store_number_of_skus+sa_gender+sa_avg_rate_of_pay+avg_income_code+avg_age_band+homeowner_ratio+child_ratio+cust_gender+post_policy*study_group, data=bms_returns)
summary(model_step)

step<-stepAIC(model_step, direction="both") #choose vars
step$anova
```
>##### Ignore recommendations

#### Check for Multicollinearity
```{r}
df1_bm<-data.frame(bms_returns$post_policy, bms_returns$study_group,log(bms_returns$monthly_sales_amt+1), log(bms_returns$store_average_price+1),log(bms_returns$store_number_of_skus+1),bms_returns$sa_gender,+log(bms_returns$sa_avg_years_of_exp+1),bms_returns$sa_avg_rate_of_pay, bms_returns$avg_income_code, bms_returns$avg_age_band,bms_returns$homeowner_ratio,bms_returns$child_ratio,bms_returns$avg_length_residence, bms_returns$cust_gender)
m1_bm<-as.matrix(cor(df1_bm))
View(m1_bm)
vif(df1_bm)
#multi-collinearity between monthly_sales_amt and store_number_of_skus & store_average_price & cust_gender, can remove all except monthly_sales_amt. Also, homeowner_ratio and child_ratio are redundant, removing child_ratio.
hist(bms_returns$homeowner_ratio)
df2_bm<-data.frame(bms_returns$post_policy,bms_returns$study_group,log(bms_returns$monthly_sales_cnt+1),bms_returns$sa_gender,log(bms_returns$sa_avg_years_of_exp+1),bms_returns$sa_avg_rate_of_pay,bms_returns$avg_income_code,bms_returns$avg_age_band,bms_returns$avg_length_residence,bms_returns$homeowner_ratio)
m2_bm<-as.matrix(cor(df2_bm))
View(m2_bm)
vif(m2_bm)
```
>##### remove sa_gender and homeowner_ratio. Using log of monthly_sales_cnt instead of amount decreases multicollinearity with other variables.

```{r}
df3_bm<-data.frame(bms_returns$post_policy, bms_returns$study_group,log(bms_returns$monthly_sales_cnt+1),log(bms_returns$sa_avg_years_of_exp+1),bms_returns$avg_income_code,bms_returns$avg_age_band)
m3_bm<-as.matrix(cor(df3_bm))
View(m3_bm)
vif(m3_bm)
```
>##### No dangerous multi-collinearity 

### OLS: Design and Refine Models
```{r}
model1_bm<-lm(log(return_amt+1)~post_policy+study_group+log(monthly_sales_cnt+1)+log(sa_avg_years_of_exp+1)+avg_income_code+avg_age_band+post_policy*study_group, data=bms_returns)
summary(model1_bm)

model2_bm<-lm(log(return_amt+1)~post_policy+study_group+log(monthly_sales_cnt+1)+log(sa_avg_years_of_exp+1)+avg_income_code+avg_age_band+avg_length_residence+post_policy*study_group, data=bms_returns)
summary(model2_bm)

anova(model1_bm, model2_bm, test="Chisq")
```
>##### Length of residence does not improve model fit

```{r}
model3_bm<-lm(log(return_amt+1)~post_policy+study_group+log(monthly_sales_cnt+1)+log(sa_avg_years_of_exp+1)+sa_avg_rate_of_pay+avg_income_code+avg_age_band+post_policy*study_group, data=bms_returns)
summary(model3_bm)

anova(model1_bm, model3_bm, test="Chisq")
```
>##### sa_avg_rate_of_pay improves fit

```{r}
modelOLSfin_bm<-model3_bm # FINAL OLS MODEL

pred<-predict(modelOLSfin_bm, type="response") 
summary(pred)
```
>##### All positive pred values - good

### Heteroscedasticity Testing
```{r}
residual1_bm=resid(modelOLSfin_bm)
plot(residual1_bm, ylab="Residuals", xlab="all vars") 
qqnorm(residual1_bm)
qqline(residual1_bm, col=1) #Not Good
plot(log(bms_returns$monthly_sales_cnt+1),residual1_bm, ylab="Residuals", xlab="log monthly_sales_cnt") # As the residual plot indicates, we have possible heteroskedasticity
gqtest(modelOLSfin_bm) #heteroskedasticity
bptest(modelOLSfin_bm) #heteroskedasticity 
```
>##### Use robust SEs
```{r}
coeftest(modelOLSfin_bm, vcov = vcovHC(modelOLSfin_bm, "HC1"))
```
>#### OLS RESULTS: Change in policy decreases return dollar amount by 36.62%

```{r}
plot(effect(term="post_policy*study_group",mod=modelOLSfin_bm,xlevel=2),multiline=TRUE)
```
>#### Although the interaction term coefficient from the data set with both study group and control group is the final result (because the difference between the study group and control group is the effect of the policy change),   we isolate the groups to check if each policy change beta is significant in case there was specification errors in the OLS model.

```{r}
sg<-subset(bms_returns, bms_returns$study_group==1)

modelOLSfin_bm_sg<-lm(log(return_amt+1)~post_policy+log(monthly_sales_cnt+1)+log(sa_avg_years_of_exp+1)+sa_avg_rate_of_pay+avg_income_code+avg_age_band, data=sg)
summary(modelOLSfin_bm_sg)

cg<-subset(bms_returns, bms_returns$study_group==0)

modelOLSfin_bm_cg<-lm(log(return_amt+1)~post_policy+log(monthly_sales_cnt+1)+log(sa_avg_years_of_exp+1)+sa_avg_rate_of_pay+avg_income_code+avg_age_band, data=cg)
summary(modelOLSfin_bm_cg)

plot(effect(term="post_policy",mod=modelOLSfin_bm_sg,xlevel=2),more = TRUE)

plot(effect(term="post_policy",mod=modelOLSfin_bm_cg,xlevel=2),more=TRUE)
```
>#### Magnitude of interaction term beta seems a bit high. Sales amount is endogenous due to simultaneity and possibly OV as well - perhaps other store attributes can serve as IVs. 

### IV Variable Assessment
```{r}
df5_bm<-data.frame(log(bms_returns$return_amt+1),log(bms_returns$monthly_sales_amt+1),bms_returns$sa_married,bms_returns$sa_full_time, bms_returns$sa_dependent, bms_returns$post_policy, bms_returns$study_group,bms_returns$sa_gender,bms_returns$sa_avg_rate_of_pay,+log(bms_returns$sa_avg_years_of_exp+1),bms_returns$avg_income_code,bms_returns$avg_age_band,bms_returns$homeowner_ratio)
m5_bm<-as.matrix(cor(df5_bm))
View(m5_bm)

df6_bm<-data.frame(log(bms_returns$return_amt+1),log(bms_returns$monthly_sales_cnt+1),bms_returns$sa_married,bms_returns$sa_dependent, bms_returns$sa_full_time, bms_returns$sa_gender, bms_returns$sa_avg_rate_of_pay, bms_returns$study_group,+log(bms_returns$sa_avg_years_of_exp+1),bms_returns$avg_income_code,bms_returns$avg_age_band,bms_returns$homeowner_ratio)
m6_bm<-as.matrix(cor(df6_bm))
mean(m6_bm)
View(m6_bm)
```
>##### No possible IV candidates 

### RETURN_CNT Models 
####Try changing the dependent variable to log return count and using Poisson/Negative Binomial
```{r}
#Sales Cnt
summary(poisson1_bm<-glm((return_cnt+1)~post_policy+study_group+log(monthly_sales_cnt+1)+log(sa_avg_years_of_exp+1)+sa_avg_rate_of_pay+avg_age_band+avg_income_code+post_policy*study_group, family="poisson", data=bms_returns))

residual2_bm=resid(poisson1_bm)
plot(residual2_bm, ylab="Residuals", xlab="")
qqnorm(residual2_bm)
qqline(residual2_bm, col=1)

with(poisson1_bm, null.deviance - deviance)
with(poisson1_bm, df.null - df.residual)
with(poisson1_bm, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
#Significant so Poisson fails

marg_means1_bm<-data.frame(post_policy=seq(0,1), study_group=seq(0,1),monthly_sales_cnt=mean(log(bms_returns$monthly_sales_cnt+1)),sa_avg_rate_of_pay=mean(bms_returns$sa_avg_rate_of_pay),avg_age_band=mean(bms_returns$avg_age_band), sa_avg_years_of_exp=mean(log(bms_returns$sa_avg_years_of_exp+1)), avg_income_code=mean(bms_returns$avg_income_code))


#Negative Binomial Model
summary(negbin1_bm<-glm.nb((return_cnt+1)~post_policy+study_group+log(monthly_sales_cnt+1)+sa_avg_rate_of_pay+avg_age_band+avg_income_code+log(sa_avg_years_of_exp+1)+post_policy*study_group, data=bms_returns))
exp(coef(negbin1_bm))

#Compare to Poisson model
with(negbin1_bm, null.deviance - deviance)
with(negbin1_bm, df.null - df.residual)
with(negbin1_bm, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
X2 <- 2 * (logLik(negbin1_bm) - logLik(poisson1_bm))
X2
pchisq(X2, df = 1, lower.tail=FALSE) # Significant Likelihood Ratio Test: Negative Binomial over Poisson
```

```{r}
#Negbin1 Analysis

#Check for hetero
residual4_bm=resid(negbin1_bm)
plot(log(bms_returns$monthly_sales_cnt+1),residual4_bm, ylab="Residuals", xlab="monthly_sales_cnt") # As the residual plot indicates, we have possible heteroskedasticity
qqnorm(residual4_bm)
qqline(residual4_bm,col=1) 
gqtest(negbin1_bm) #heteroscedasticity
bptest(negbin1_bm) #heteroscedasticity
```

```{r}

# Robust SEs
coeftest(negbin1_bm, vcov = vcovHC(negbin1_bm, "HC1")) #interaction term still significant

cov.negbin1_bm <- vcovHC(negbin1_bm, type="HC1")
s <- deltamethod(list(~ exp(x1), ~ exp(x2), ~ exp(x3), ~ exp(x4), ~ exp(x5), ~ exp(x6), ~ exp(x7), ~ exp(x8), ~ exp(x9)), coef(negbin1_bm),cov.negbin1_bm)
std.err <- sqrt(diag(cov.negbin1_bm))
r.est <- cbind(Estimate= coef(negbin1_bm), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(negbin1_bm)/std.err), lower.tail=FALSE),
LL = coef(negbin1_bm) - 1.96 * std.err,
UL = coef(negbin1_bm) + 1.96 * std.err)
rexp.est <- exp(r.est[, -3])-1 # exponentiate old estimates dropping the p values. minus 1 to see as difference not a factor
rexp.est[, "Robust SE"] <- s # replace SEs with estimates for exponentiated coefficients
rexp.est
#***NEGBIN MODEL CONCLUSION: Policy change decreases number of returns by 25.86%

plot(effect(term="post_policy*study_group",mod=negbin1_bm,xlevel=2),multiline=TRUE)
```

```{r}
#Control Group Isolation}
bms_returns_cg<-subset(bms_returns, study_group==0)

summary(negbin_cg<-glm.nb((return_cnt+1)~post_policy+log(monthly_sales_cnt+1)+sa_avg_rate_of_pay+avg_age_band+avg_income_code+log(avg_length_residence+1), data=bms_returns_cg))

#use robust SE:
coeftest(negbin_cg, vcov = vcovHC(negbin_cg, "HC1")) #post_policy still significant

cov.negbin_cg <- vcovHC(negbin_cg, type="HC1")
s <- deltamethod(list(~ exp(x1), ~ exp(x2), ~ exp(x3), ~ exp(x4), ~ exp(x5), ~ exp(x6), ~ exp(x7)), coef(negbin_cg),cov.negbin_cg)
std.err <- sqrt(diag(cov.negbin_cg))
r.est <- cbind(Estimate= coef(negbin_cg), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(negbin_cg)/std.err), lower.tail=FALSE),
LL = coef(negbin_cg) - 1.96 * std.err,
UL = coef(negbin_cg) + 1.96 * std.err)
rexp.est <- exp(r.est[, -3])-1 # exponentiate old estimates dropping the p values
rexp.est[, "Robust SE"] <- s # replace SEs with estimates for exponentiated coefficients
rexp.est
#demonstrate IRRs. The output indicates an increase in returns (due to environmental control factors) of 19.02% in the control group

plot(effect(term="post_policy",mod=negbin_cg,xlevel=2),multiline=TRUE)
```

```{r}
#Study Group Isolation}
bms_returns_sg<-subset(bms_returns, study_group==1)

summary(negbin_sg<-glm.nb((return_cnt+1)~post_policy+log(monthly_sales_cnt+1)+sa_avg_rate_of_pay+avg_age_band+avg_income_code+log(avg_length_residence+1), data=bms_returns_sg))

#use robust SE:
coeftest(negbin_sg, vcov = vcovHC(negbin_sg, "HC1")) #post_policy still significant

cov.negbin_sg <- vcovHC(negbin_sg, type="HC1")
s <- deltamethod(list(~ exp(x1), ~ exp(x2), ~ exp(x3), ~ exp(x4), ~ exp(x5), ~ exp(x6), ~ exp(x7)), coef(negbin_sg),cov.negbin_sg)
std.err <- sqrt(diag(cov.negbin_sg))
r.est <- cbind(Estimate= coef(negbin_sg), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(negbin_sg)/std.err), lower.tail=FALSE),
LL = coef(negbin_sg) - 1.96 * std.err,
UL = coef(negbin_sg) + 1.96 * std.err)
rexp.est <- exp(r.est[, -3])-1 # exponentiate old estimates dropping the p values
rexp.est[, "Robust SE"] <- s # replace SEs with estimates for exponentiated coefficients
rexp.est
#demonstrate IRRs. The output  indicates that policy change in the study group decreases returns by 11.17% 
plot(effect(term="post_policy",mod=negbin_sg,xlevel=2),multiline=TRUE)


#***Q4 FINAL CONCLUSION: Policy change leads to 25.86% decrease in the number of returns and a 36.62% decrease in the return dollar amount for bms channel
```
