---
title: "Return Policy Effect Online"
author: Greg Murray
---

# Return Policy Change Impact on Online Returns.
#dependent variable=return_amt; key independent variables=post_policy,study_group, post_policy*studygroup 

### Libraries and Dependencies
```{r}
library(QuantPsyc)
library(effects)
library(MASS)
library(usdm)
library(lmtest)
library(AER)
library(foreign)
library(aod)
library(ggplot2)
library(sandwich)
library(VIF)
library(msm)
```

### Data Initialization
```{r}
setwd('c:/users/greg/r_projects/bus_analytics_project')
onl_returns<-read.csv('onl_store_data2.csv')
summary(onl_returns)
onl_returns<-na.omit(onl_returns)
```
### Raw Data Analysis
```{r}
hist(onl_returns$return_amt)
hist(log(onl_returns$return_amt+1))#
hist(log(onl_returns$daily_sales_amt+1))
hist(log(onl_returns$daily_sales_amt+1))#
hist(onl_returns$daily_sales_cnt)
hist(log(onl_returns$daily_sales_cnt+1))#
hist(onl_returns$store_number_of_skus)
hist(log(onl_returns$store_number_of_skus))#
hist(onl_returns$sa_avg_years_of_exp)
hist(log(onl_returns$sa_avg_years_of_exp))#
hist(onl_returns$avg_length_residence)#
hist(log(onl_returns$avg_length_residence))
hist(onl_returns$cust_gender) 
hist(log(onl_returns$cust_gender))#
hist(onl_returns$homeowner_ratio) 
hist(log(onl_returns$homeowner_ratio+1))#
hist(onl_returns$child_ratio) #
hist(log(onl_returns$child_ratio+1))
```

#### Raw data plots with dependent var
```{r}
sg<-subset(onl_returns, study_group==1)
cg<-subset(onl_returns, study_group==0)
boxplot(log(sg$return_amt+1)~sg$post_policy,xlab="post_policy (study group)")
```
>##### Returns go down after policy change in the study group (sans regression modelling)

```{r}
boxplot(log(cg$return_amt+1)~cg$post_policy,xlab="post_policy (control group")
```
>##### Returns go down up slightly after policy change in the control group (sans regression modelling)

```{r}
plot(log(onl_returns$daily_sales_amt+1), log(onl_returns$return_amt+1))
plot(log(onl_returns$daily_sales_cntt+1), log(onl_returns$return_amt+1))
plot(onl_returns$store_average_price, log(onl_returns$return_amt+1))
plot(onl_returns$store_number_of_skus, log(onl_returns$return_amt+1))
boxplot(log(onl_returns$return_amt+1)~onl_returns$sales_volume_group, xlab="sales volume group")
plot(onl_returns$avg_length_residence, log(onl_returns$return_amt+1))
plot(log(onl_returns$homeowner_ratio), log(onl_returns$return_amt+1))
plot(onl_returns$child_ratio, log(onl_returns$return_amt+1))
boxplot(log(onl_returns$return_amt+1)~onl_returns$avg_income_code, xlab="avg income code")
boxplot(log(onl_returns$return_amt+1)~onl_returns$avg_age_band, xlab="avg age band")
boxplot(log(onl_returns$return_amt+1)~onl_returns$, xlab="avg income code")
```

#### Stepwise Control Variable Selection
```{r}
OLSModel<-lm(log(return_amt+1)~post_policy+study_group+log(daily_sales_amt+1)+log(store_average_price+1)+log(store_number_of_skus+1)+sales_volume_group+avg_income_code+log(homeowner_ratio+1)+child_ratio+avg_age_band+cust_gender+post_policy*study_group, data=onl_returns)

step<-stepAIC(OLSModel, direction="both") #choose vars
step$anova

model_step<-lm(log(return_amt+1)~post_policy+study_group+log(daily_sales_amt+1)+store_average_price+log(store_number_of_skus+1)+sales_volume_group+log(homeowner_ratio+1)+avg_income_code+avg_age_band+cust_gender+post_policy*study_group, data=onl_returns)
```
>##### Ignore recommendations

#### Check for Multicollinearity
```{r}
df<-data.frame(onl_returns$post_policy, onl_returns$study_group, log(onl_returns$daily_sales_amt+1), onl_returns$store_average_price, onl_returns$store_number_of_skus, onl_returns$sales_volume_group, onl_returns$avg_income_code, log(onl_returns$homeowner_ratio+1),onl_returns$child_ratio, onl_returns$avg_age_band, onl_returns$cust_gender)
m1_onl<-as.matrix(cor(df))
View(m1_onl)
vif(df)
```
>##### multi-collinearity between daily_sales_amt and store_number_of_skus & store_average_price, child_ratio, homeowner_ratio & sales_volume_group. Also, study_group and cust_gender.

>##### Can possibly use ave_length_residence to measure homeowners (people don't typically live in the same apartment for a long time)
df2_onl<-data.frame(onl_returns$post_policy, onl_returns$study_group, log(onl_returns$daily_sales_amt+1),onl_returns$avg_income_code, onl_returns$avg_age_band)

m2_onl<-as.matrix(cor(df2_onl))
View(m2_onl)
vif(df2)
```
>##### No dangerous multi-collinearity

### OLS: Design and Refine Models
```{r}
model1_onl<-lm(log(return_amt+1)~post_policy+study_group+log(daily_sales_amt+1)+avg_income_code+avg_age_band+post_policy*study_group, data=onl_returns)
summary(model1_onl)
#insignificant interaction beta - as expected

model2_onl<-lm(log(return_amt+1)~post_policy+study_group+log(daily_sales_amt+1)+avg_income_code+avg_age_band+avg_length_residence+post_policy*study_group, data=onl_returns)
summary(model2_onl)

anova(model1_onl, model2_onl, test="Chisq")
#Do not add avg_length of residence

modelOLSfin_onl<-model1_onl
```

#### Heteroscedasticity Testing
```{r}
residual1=resid(modelOLSfin_onl)
qqnorm(residual1)
qqline(residual1, col=1) 
plot(residual1, ylab="Residuals", xlab="all resids")
plot(log(onl_returns$daily_sales_amt+1),residual1, ylab="Residuals", xlab="daily_sales_amt") # As the residual plot indicates, residual weirdness we have possible heteroskedasticity
gqtest(modelOLSfin_onl) #no heteroskedasticity
bptest(modelOLSfin_onl) #heteroskedasticity 
```
>##### Use robust SEs
```{r}
cov.modelOLSfin_onl<- vcovHC(modelOLSfin_onl, type="HC1")
```

### **OLS MODEL CONCLUSION: Insignificant interaction term, policy change has no effect on returns for online channel**

### 2SLS Model Approach
```{r}
df3_onl<-data.frame(log(onl_returns$return_amt+1),log(onl_returns$daily_sales_amt+1),onl_returns$store_average_price,onl_returns$store_number_of_skus, onl_returns$sales_volume_group,onl_returns$avg_length_residence, onl_returns$post_policy, onl_returns$study_group,onl_returns$avg_income_code, onl_returns$avg_age_band)
m3_onl<-as.matrix(cor(df3_onl))
mean(m3_onl)
View(m3_onl)

df4_onl<-data.frame(log(onl_returns$return_amt+1),log(onl_returns$daily_sales_amt+1),onl_returns$store_number_of_skus, onl_returns$sales_volume_group,onl_returns$avg_length_residence,onl_returns$child_ratio, onl_returns$post_policy, onl_returns$study_group,onl_returns$avg_income_code, onl_returns$avg_age_band)
m4_onl<-as.matrix(cor(df4_onl))
```

#### Try sales_volume group and store_number_of_skus as IVs for daily_sales_amount
```{r}
ivregmodel_onl<-ivreg(log(return_amt+1)~post_policy+study_group+log(daily_sales_amt+1)+avg_income_code+avg_age_band+post_policy*study_group|sales_volume_group+store_number_of_skus+post_policy+study_group+avg_income_code+avg_age_band+post_policy*study_group, data=onl_returns)
summary(ivregmodel_onl,diagnostics = TRUE)
#With F-statistic signficant the IVs relevance assumption holds, Sargan insigificant the exogeneity assumption holds but Wu-Hausman insignificant means there was no endogeneity in the OLS model
```

## RETURN_CNT Models 
### Poisson Model
```{r}
colnames(onl_returns)[11]<-"return_cnt"

summary(poisson1<-glm((return_cnt+1)~post_policy+study_group+log(daily_sales_cnt+1)+avg_income_code+avg_age_band+post_policy*study_group, family="poisson", data=onl_returns))

with(poisson1, null.deviance - deviance)
with(poisson1, df.null - df.residual)
with(poisson1, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))
```
>##### Significant so Poisson fails

### Negative Binomial Model
```{r}
marg_means<-data.frame(post_policy=seq(0,1), study_group=seq(0,1), avg_income_code=mean(onl_returns$avg_income_code),avg_age_band=mean(onl_returns$avg_age_band),daily_sales_cnt=mean(log(onl_returns$daily_sales_cnt+1)))

predict(poisson1, marg_means, type="response", se.fit=TRUE)

summary(negbin1_ol<-glm.nb((return_cnt+1)~post_policy+study_group+log(daily_sales_cnt+1)+avg_age_band+avg_income_code+avg_age_band+post_policy*study_group, data=onl_returns))
```

#### Heteroscedasticity
```{r}
residual3=resid(negbin1_ol)
plot(log(onl_returns$daily_sales_cnt+1),residual3, ylab="Residuals", xlab="daily_sales_cnt") # As the residual plot indicates, we have possible heteroskedasticity
qqnorm(residual3)
qqline(residual3, col=1)
gqtest(negbin1_ol)#hetero
bptest(negbin1_ol)#hetero

with(negbin1_ol, null.deviance - deviance)
with(negbin1_ol, df.null - df.residual)
with(negbin1_ol, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

X2 <- 2 * (logLik(negbin1_ol) - logLik(poisson1))
X2
pchisq(X2, df = 1, lower.tail=FALSE) # Negative Binomial over Poisson
```

#### Robust SEs
```{r}
coeftest(negbin1_ol, vcov = vcovHC(negbin1_ol, "HC1"))

cov.negbin1_ol <- vcovHC(negbin1_ol, type="HC1")
s <- deltamethod(list(~ exp(x1), ~ exp(x2), ~ exp(x3), ~ exp(x4), ~ exp(x5), ~ exp(x6), ~ exp(x7)), coef(negbin1_ol),cov.negbin1_ol)
std.err <- sqrt(diag(cov.negbin1_ol))
r.est <- cbind(Estimate= coef(negbin1_ol), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(negbin1_ol)/std.err), lower.tail=FALSE),
LL = coef(negbin1_ol) - 1.96 * std.err,
UL = coef(negbin1_ol) + 1.96 * std.err)
rexp.est <- exp(r.est[, -3]) # exponentiate old estimates dropping the p values
rexp.est[, "Robust SE"] <- s # replace SEs with estimates for exponentiated coefficients
rexp.est 

plot(effect(term="post_policy*study_group",mod=negbin1_ol,xlevel=2),multiline=TRUE)
```
>### **NEGBIN CONCLUSION: Interaction term is insignificant - policy change likely has no effect on returns in online channel**

### Control Group Isolation
```{r}
control_group<-subset(onl_returns, study_group==0)
summary(onl_returns)
summary(negbin_cg<-glm.nb((return_cnt+1)~post_policy+log(daily_sales_cnt+1)+avg_income_code+avg_age_band, data=control_group))
```
>##### Control group coeffecient is insignificant

#### Heteroscedasticity
```{r}
residual4=resid(negbin_cg)
qqnorm(residual4)
qqline(residual4, col=1)
gqtest(negbin_cg) #no hetero
bptest(negbin_cg)#hetero
```
>##### use robust SE
```{r}
coeftest(negbin_cg, vcov = vcovHC(negbin_cg, "HC1"))

cov.negbin_cg <- vcovHC(negbin_cg, type="HC1")
s <- deltamethod(list(~ exp(x1), ~ exp(x2), ~ exp(x3), ~ exp(x4), ~ exp(x5)), coef(negbin_cg),cov.negbin_cg)
std.err <- sqrt(diag(cov.negbin_cg))
r.est <- cbind(Estimate= coef(negbin_cg), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(negbin_cg)/std.err), lower.tail=FALSE),
LL = coef(negbin_cg) - 1.96 * std.err,
UL = coef(negbin_cg) + 1.96 * std.err)
rexp.est <- exp(r.est[, -3]) # exponentiate old estimates dropping the p values
rexp.est[, "Robust SE"] <- s # replace SEs with estimates for exponentiated coefficients
rexp.est 
```
>#### Beta for post_policy is insignicant, therefore without a control group there is no way to isolate the policy change effect in the study group.

## **FINAL CONCLUSION:** 
>## **Policy change likely has no effect on returns in online channel**
